Demanding Resources: Converging Perceptions of Challenge and Resource Characteristics

### 2023-08-12 SIOP2024/SIOP2024convergence.Rmd
updating siop project

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
 Using the Challenge-Hindrance Framework, 2 research questions were examined: are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic. A survey of 568 workers rated job characteristics in terms of relevance as well as perceptions as challenges, hindrances and resources using the common O\*NET classification of work activities and context.The findings point to high association between the number of resources and challenge demands employees experience, reasonable correspondence or agreement that a characteristic is a resource *and* challenge, and differences in this association by job characteristic category. More variability was observed when exploring associations between resources and hindrance stressors, and challenge/hindrance stressors.

keywords          : "keywords"
wordcount         : "X"

@@

```
The Occupational Information Network (O\*NET; onetonline.org) contains a reasonably comprehensive description of occupations [@peterson2001understanding] which subject matter experts inform via surveys. We utilize a set of O\*NET job context and activity statements contained in these surveys to explore a series of research questions about how people perceive resources, challenges, and hindrances within their jobs. There are a number of advantage to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope. Here, we focus broadly on two research questions using these O\*NET items: 1) are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic (e.g., interacting with others vs. physical work characteristics)? A brief summary of the Challenge-hindrance Framework is presented prior to rationale for these specific questions.

@@

We argue below that *perception* of something as a resource or demand matters. Although the word “stress” often carries a negative connotation, the "father" of the current concept, @selye1936syndrome, conceptualized stress much less pejoratively - rather thinking of it as a *response to change*. For instance, consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event. One may appraise the nomination as a negative stressor. However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired. Selye the physician would likely have labeled the two responses as subjective manifestations of "distress", and "eustress" [@selye1974stress]. In modern I-O Psychology parlance (and more consistent with the job demands-resources model [@demerouti2001job] and job demands-resources theory [@bakker2017job]), the two workers would both be characterized as appraising the speaking opportunity as a job demand, but one would be appraising the demand as a *challenge* while the other would appraise the demand as a *hindrance* [@cavanaugh2000empirical]. According to @cavanaugh2000empirical, challenge demands promote mastery, personal growth, and future gains. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes [e.g., @cavanaugh2000empirical].

At the most broad level, we can question whether employees actually distinguish between challenges and hindrances as the theory describes. Research suggests that people can and do perceive them differently. For example, @bakker2013weekly found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand. @webster2011extending also considered three common work characteristics including workload, role ambiguity, and role conflict. Interestingly, they found that while each could be identified *primarily* as a challenge or hindrance, employees could also appraise that a characteristic is simultaneously both a challenge and hindrance. However, this list of demands (workload, role ambiguity, and role conflict) is somewhat narrow. Using a very wide range of O\*NET job characteristics regarding job context and activities, we explore whether challenges (positive stressors per the definition above) might actually be positively related to resources. Per the job demands-resources theory [@bakker2017job] resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. It stands to reason that a challenging demand may be considered a resource.

*RQ1*: Do employees who perceive many resources in their jobs also perceived many challenges?

@@

Research Question 1 explored whether people who perceive many challenges in their work also report many resources. The results show that the total number of undifferentiated challenges and resources are positively related. In fact, table \@ref(tab:cortab) shows a very high association between resources and challenges (*r* = .86). This association, however, only captures the relationship between these demands and resources in *sheer volume*. That is, Table \@ref(tab:cortab) operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job. This correlational analysis *does* imply that workers who experience more resources also perceive greater challenges. Although not explicitly part of the above research question, we also explored the associations between resources and hindrances (*r* = .23) and challenges and hindrances (*r* = .22), which were also significantly positive with moderate in magnitude, suggesting that some of this "sheer volume" may be capturing job complexity (that is, the more complex the job, the more characteristics are relevant, and therefore the more likely it is to have *more* challenges as well as *more* hindrances as well as *more* resources). Although we did not address job complexity as a moderator in the current paper, we do plan to do so in future investigations. Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (*M* = 13.09) than both resources and challenges.

>>>>

#authornote: |
#  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

#  Enter author note here.

abstract: |
 Using the Challenge-Hindrance Framework, 2 research questions were examined: are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic. A survey of 568 workers rated job characteristics in terms of relevance as well as perceptions as challenges, hindrances and resources using the common O\*NET classification of work activities and context.The findings point to high association between the number of resources and challenge demands employees experience, reasonable correspondence or agreement that a characteristic is a resource *and* challenge, and differences in this association by job characteristic category. More variability was observed when exploring associations between resources and hindrance stressors, and challenge/hindrance stressors. **WORD LIMITS: Title (85 characters); Abstract (600 characters); Word limit (3,000; exclude tables, figures, references)**

#keywords          : "keywords"
#wordcount         : "X"

@@

```
The Occupational Information Network ([O\*NET](onetonline.org)) contains a large yet non-exhaustive description of occupations [@peterson2001understanding] which subject matter experts inform via surveys. In the current study, we retain a set of O\*NET job context and activity statements to explore questions about how people perceive resources, challenges, and hindrances within their jobs.^[There are a number of advantages to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.] Here, we focus broadly on two research questions: 1) do challenging jobs tend to be resource-rich or -poor?, and 2) is that association be moderated by job characteristic (e.g., social vs. physical aspects of work)?

Although the word *stress* often carries a negative connotation, the "father" of the current concept, @selye1936syndrome, conceptualized the construct much less pejoratively - simply presenting it as a *response to change*. Consider, for example, the responses two different employees may have to being nominated to give a presentation at an upcoming company event. One may appraise the nomination as a frightful task whereas another may appraise it as an exciting opportunity to share their experiences with their coworkers. Selye the physician would likely label the two responses as subjective manifestations of "distress" and "eustress" [@selye1974stress].

@@

In modern I-O psychology parlance, and more consistent with the job demands-resources model and job demands-resources theory [e.g., @bakker2017job; @demerouti2001job], the two workers would both be characterized as appraising the speaking opportunity as a job demand, which would be *stressful*. However, @cavanaugh2000empirical's challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people *feel* about a given stressor. One of our above employees would be appraising the demand as a *challenge* while the other would appraise the demand as a *hindrance* [@cavanaugh2000empirical]. @horan2020review state that “…stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees” (p. 3). According to @cavanaugh2000empirical, challenge demands promote mastery, personal growth, and future gains - these should lead to coping strategies that facilitate achievement and motivation [e.g., @kim2020thriving]. Hindrance demands (e.g., role conflict, workplace politics), in contrast, inhibit growth, learning and goal achievement. Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes [e.g., @cavanaugh2000empirical].

@lepine2022challenge explains the mechanisms by which demands are related to these differential positive and negative outcomes. Similar to the job-demands resources theory [@bakker2017job], challenge and hindrance demands elicit two different paths or processes. Challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result. Of note, however, this energy may be depleted eventually, leading to strain. Hindrance stressors elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This is a result of depleted resources via frustrations and other affectively negative reactions [@lepine2022challenge].

Recently, @horan2020review,  @lepine2022challenge, and @mazzola2019should have all called out the need for additional research to incorporate the appraisal process into the challenge-hindrance stressor framework. In the current study, we build on the work of this growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources *and* demands [@webster2011extending].

## Current Study and Research Questions

At the broadest level, we can question whether employees actually distinguish between challenges and hindrances as the theory describes. Research suggests that people can and do. For example, @bakker2013weekly found that work pressure is classified as a hindrance demand, while the requirement to express emotions is a challenge demand. @webster2011extending also considered three common work characteristics including workload, role ambiguity, and role conflict. Interestingly, they found that while each could be identified *primarily* as a challenge or hindrance, employees could also appraise that a characteristic is simultaneously both a challenge and hindrance. Here we note that this list of demands (workload, role ambiguity, and role conflict) is quite narrow.

Using a very large set of O\*NET job characteristics, we explore whether challenges (positive stressors per the definition above) might actually be simultaneously viewed as resources. Per the job demands-resources theory [@bakker2017job] resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [@demerouti2001job]. It stands to reason that some challenging demands may also be appraised as resources.

*RQ1*: Are challenging demands also appraised as resources?

@@

Research Question 1 explored whether challenging demands may also be commonly appraised as resources. The results show that the total number of undifferentiated challenges and resources are positively related. In fact, table \@ref(tab:cortab) shows a very high association between resources and challenges (*r* = .86). This association, however, only captures the relationship between these demands and resources in *sheer volume*. That is, Table \@ref(tab:cortab) operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job. This correlational analysis *does* imply that workers who experience more resources also perceive greater challenges. Although not explicitly part of the above research question, we also explored the associations between resources and hindrances (*r* = .23) and challenges and hindrances (*r* = .22), which were also significantly positive with moderate in magnitude, suggesting that some of this "sheer volume" may be capturing job complexity (that is, the more complex the job, the more characteristics are relevant, and therefore the more likely it is to have *more* challenges as well as *more* hindrances as well as *more* resources). Although we did not address job complexity as a moderator in the current paper, we do plan to do so in future investigations. Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (*M* = 13.09) than both resources (*M* = 36.02) and challenges (*M* = 35.64).

### 2023-08-12 SIOP2024/SIOP2024convergence.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  jou]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\usepackage{dblfloatfix}

\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Demanding Resources: Converging Perceptions of Challenge and Resource Characteristics},
  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
Using the Challenge-Hindrance Framework, 2 research questions were examined: are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic. A survey of 568 workers rated job characteristics in terms of relevance as well as perceptions as challenges, hindrances and resources using the common O*NET classification of work activities and context.The findings point to high association between the number of resources and challenge demands employees experience, reasonable correspondence or agreement that a characteristic is a resource \emph{and} challenge, and differences in this association by job characteristic category. More variability was observed when exploring associations between resources and hindrance stressors, and challenge/hindrance stressors.
}

@@

The Occupational Information Network (O*NET; onetonline.org) contains a reasonably comprehensive description of occupations (Peterson et al., 2001) which subject matter experts inform via surveys. In the current study, we utilize a set of O*NET job context and activity statements to explore two questions about how people perceive resources, challenges, and hindrances within their jobs. \footnote{There are a number of advantages to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.} Here, we focus broadly on two research questions using these O*NET items: 1) are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic (e.g., interacting with others vs.~physical work characteristics)? The basis for these questions comes out the stress literature (e.g., Lazarus \& Folkman, 1984).

We argue below that \emph{perception} of something as a resource or demand matters. Although the word ``stress'' often carries a negative connotation, the ``father'' of the current concept, Selye (1936), conceptualized stress much less pejoratively - rather thinking of it as a \emph{response to change}. For instance, consider the different reactions two different employees may have to being nominated to give a speech at an upcoming company event. One may appraise the nomination as a negative stressor. However, another employee may appraise the nomination to do so as an opportunity to share their experiences with more of their coworkers, or one in which they may receive recognition they have desired. Selye the physician would likely have labeled the two responses as subjective manifestations of ``distress'', and ``eustress'' (Selye, 1974).

@@

In modern I-O psychology parlance (and more consistent with the job demands-resources model (Demerouti et al., 2001) and job demands-resources theory (Bakker \& Demerouti, 2017)), the two workers above would both be characterized as appraising the speaking opportunity as a job demand. However, as noted above, demands/stressors are subjective. Cavanaugh's (2000) challenge-hindrance stressor framework speaks directly to this reality, and suggests that the way we understand reactions to stressors requires consideration of how people \emph{feel} about a given stressor. One of our above employees would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000). According to Cavanaugh et al. (2000), challenge demands promote mastery, personal growth, and future gains. Challenge stressors should lead to coping strategies that facilitate achievement and motivation (e.g., Kim \& Beehr, 2020). Hindrance demands, in contrast, inhibit growth, learning and goal achievement (e.g., perception of role conflict, workplace politics). Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).

LePine (2022) explain the mechanisms by which demands are related to these differential positive and negative outcomes. Similar to the job-demands resources theory (Bakker \& Demerouti, 2017), challenge and hindrance demands elicit two different paths or processes. Challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result. Engagement is positively related to the positive outcomes described above: motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. Rosen et al. (2020), in fact, suggests that appraisals may change over time, which is probably expected when thinking about how workers experience continued stressors. Hindrance stressors elicit a different process. Rather than experiencing engagement, disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This is a result of depleted resources via frustrations and other affectively negative reactions (LePine, 2022).

Recently, Horan et al. (2020) and LePine (2022) have both called out the need for additional research to incorporate the \emph{appraisal process} described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources into our study of the overarching job demands-resources model. In fact, Horan et al. (2020) state that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3). In the current study, we build on the work of a growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources \emph{and} demands (Webster et al., 2011).

@@

At the most broad level, we can question whether employees actually distinguish between challenges and hindrances as the theory describes. Research suggests that people can and do perceive them differently. For example, Bakker and Sanz-Vergel (2013) found that perceived work pressure can be classified as a hindrance demand, while the requirement to express emotions is a challenge demand. Webster et al. (2011) also considered three common work characteristics including workload, role ambiguity, and role conflict. Interestingly, they found that while each could be identified \emph{primarily} as a challenge or hindrance, employees could also appraise that a characteristic is simultaneously both a challenge and hindrance. However, this list of demands (workload, role ambiguity, and role conflict) is somewhat narrow. Using a very wide range of O*NET job characteristics regarding job context and activities, we explore whether challenges (positive stressors per the definition above) might actually be positively related to resources. Per the job demands-resources theory (Bakker \& Demerouti, 2017) resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). It stands to reason that a challenging demand may be considered a resource.

\emph{RQ1}: Do employees who perceive many resources in their jobs also perceived many challenges?
\emph{Amend the wording to fit the lead up}

@@

\begin{table*}[tbp]

@@

\end{table*}

@@

Research Question 1 explored whether people who perceive many challenges in their work also report many resources. The results show that the total number of undifferentiated challenges and resources are positively related. In fact, table \ref{tab:cortab} shows a very high association between resources and challenges (\emph{r} = .86). This association, however, only captures the relationship between these demands and resources in \emph{sheer volume}. That is, Table \ref{tab:cortab} operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job. This correlational analysis \emph{does} imply that workers who experience more resources also perceive greater challenges. Although not explicitly part of the above research question, we also explored the associations between resources and hindrances (\emph{r} = .23) and challenges and hindrances (\emph{r} = .22), which were also significantly positive with moderate in magnitude, suggesting that some of this ``sheer volume'' may be capturing job complexity (that is, the more complex the job, the more characteristics are relevant, and therefore the more likely it is to have \emph{more} challenges as well as \emph{more} hindrances as well as \emph{more} resources). Although we did not address job complexity as a moderator in the current paper, we do plan to do so in future investigations. Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (\emph{M} = 13.09) than both resources and challenges.

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-rosen2020challenges}{}}%
Rosen, C. C., Dimotakis, N., Cole, M. S., Taylor, S. G., Simon, L. S., Smith, T. A., \& Reina, C. S. (2020). When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes. \emph{Journal of Applied Psychology}, \emph{105}(10), 1181.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Demanding Resources: Converging Perceptions of Challenge and Resource Characteristics},
  pdfauthor={John Kulas1, Alicia Stachowski2, \& Renata García Prieto Palacios Roji3},
  pdflang={en-EN},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\abstract{%
Using the Challenge-Hindrance Framework, 2 research questions were examined: are jobs with many resources also perceived to have many challenges, and 2) could that association be moderated by kind of job characteristic. A survey of 568 workers rated job characteristics in terms of relevance as well as perceptions as challenges, hindrances and resources using the common O*NET classification of work activities and context.The findings point to high association between the number of resources and challenge demands employees experience, reasonable correspondence or agreement that a characteristic is a resource \emph{and} challenge, and differences in this association by job characteristic category. More variability was observed when exploring associations between resources and hindrance stressors, and challenge/hindrance stressors. \textbf{WORD LIMITS: Title (85 characters); Abstract (600 characters); Word limit (3,000; exclude tables, figures, references)}
}

@@

The Occupational Information Network (\href{onetonline.org}{O*NET}) contains a large yet non-exhaustive description of occupations (Peterson et al., 2001) which subject matter experts inform via surveys. In the current study, we retain a set of O*NET job context and activity statements to explore questions about how people perceive resources, challenges, and hindrances within their jobs.\footnote{There are a number of advantages to using this standard set of statements, but the primary one here lies in our ability to consider a wide range of job characteristics, with a focus on individual perceptions of each rather than limiting ourselves to a more generic set of demands or those of a limited scope.} Here, we focus broadly on two research questions: 1) do challenging jobs tend to be resource-rich or -poor?, and 2) is that association be moderated by job characteristic (e.g., social vs.~physical aspects of work)?

Although the word \emph{stress} often carries a negative connotation, the ``father'' of the current concept, Selye (1936), conceptualized the construct much less pejoratively - simply presenting it as a \emph{response to change}. Consider, for example, the responses two different employees may have to being nominated to give a presentation at an upcoming company event. One may appraise the nomination as a frightful task whereas another may appraise it as an exciting opportunity to share their experiences with their coworkers. Selye the physician would likely label the two responses as subjective manifestations of ``distress'' and ``eustress'' (Selye, 1974).

@@

In modern I-O psychology parlance, and more consistent with the job demands-resources model and job demands-resources theory (e.g., Bakker \& Demerouti, 2017; Demerouti et al., 2001), the two workers would both be characterized as appraising the speaking opportunity as a job demand, which would be \emph{stressful}. However, Cavanaugh et al. (2000)'s challenge-hindrance stressor framework suggests that the way we understand reactions to stressors requires consideration of how people \emph{feel} about a given stressor. One of our above employees would be appraising the demand as a \emph{challenge} while the other would appraise the demand as a \emph{hindrance} (Cavanaugh et al., 2000). Horan et al. (2020) state that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3). According to Cavanaugh et al. (2000), challenge demands promote mastery, personal growth, and future gains - these should lead to coping strategies that facilitate achievement and motivation (e.g., Kim \& Beehr, 2020). Hindrance demands (e.g., role conflict, workplace politics), in contrast, inhibit growth, learning and goal achievement. Perhaps not surprisingly, challenge demands are typically associated with positive outcomes, whereas hindrance demands are associated with more negative outcomes (e.g., Cavanaugh et al., 2000).

LePine (2022) explains the mechanisms by which demands are related to these differential positive and negative outcomes. Similar to the job-demands resources theory (Bakker \& Demerouti, 2017), challenge and hindrance demands elicit two different paths or processes. Challenge stressors typically result in a challenge appraisal, and engagement is likely to happen as a result. Of note, however, this energy may be depleted eventually, leading to strain. Hindrance stressors elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This is a result of depleted resources via frustrations and other affectively negative reactions (LePine, 2022).

Recently, Horan et al. (2020), LePine (2022), and Mazzola and Disselhorst (2019) have all called out the need for additional research to incorporate the appraisal process into the challenge-hindrance stressor framework. In the current study, we build on the work of this growing number of researchers who argue that the characteristics of work may be appraised simultaneously as resources \emph{and} demands (Webster et al., 2011).

@@

At the broadest level, we can question whether employees actually distinguish between challenges and hindrances as the theory describes. Research suggests that people can and do. For example, Bakker and Sanz-Vergel (2013) found that work pressure is classified as a hindrance demand, while the requirement to express emotions is a challenge demand. Webster et al. (2011) also considered three common work characteristics including workload, role ambiguity, and role conflict. Interestingly, they found that while each could be identified \emph{primarily} as a challenge or hindrance, employees could also appraise that a characteristic is simultaneously both a challenge and hindrance. Here we note that this list of demands (workload, role ambiguity, and role conflict) is quite narrow.

Using a very large set of O*NET job characteristics, we explore whether challenges (positive stressors per the definition above) might actually be simultaneously viewed as resources. Per the job demands-resources theory (Bakker \& Demerouti, 2017) resources are defined as physical, psychological, social, or organizational aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (Demerouti et al., 2001). It stands to reason that some challenging demands may also be appraised as resources.

\emph{RQ1}: Are challenging demands also appraised as resources?

@@

\begin{table}[tbp]

@@

\end{table}

@@

Research Question 1 explored whether challenging demands may also be commonly appraised as resources. The results show that the total number of undifferentiated challenges and resources are positively related. In fact, table \ref{tab:cortab} shows a very high association between resources and challenges (\emph{r} = .86). This association, however, only captures the relationship between these demands and resources in \emph{sheer volume}. That is, Table \ref{tab:cortab} operationalized each variable as the sheer number of resources, hindrances, or challenges that a respondent indicated were present within their job. This correlational analysis \emph{does} imply that workers who experience more resources also perceive greater challenges. Although not explicitly part of the above research question, we also explored the associations between resources and hindrances (\emph{r} = .23) and challenges and hindrances (\emph{r} = .22), which were also significantly positive with moderate in magnitude, suggesting that some of this ``sheer volume'' may be capturing job complexity (that is, the more complex the job, the more characteristics are relevant, and therefore the more likely it is to have \emph{more} challenges as well as \emph{more} hindrances as well as \emph{more} resources). Although we did not address job complexity as a moderator in the current paper, we do plan to do so in future investigations. Also, take note of the average numbers of resources, challenges, and hindrances cited by our sample, where these respondents generally experienced fewer hindrances in their jobs (\emph{M} = 13.09) than both resources (\emph{M} = 36.02) and challenges (\emph{M} = 35.64).

@@

\leavevmode\vadjust pre{\hypertarget{ref-mazzola2019should}{}}%
Mazzola, J. J., \& Disselhorst, R. (2019). Should we be {``challenging''} employees?: A critical review and meta-analysis of the challenge-hindrance model of stress. \emph{Journal of Organizational Behavior}, \emph{40}(8), 949--961.

@@
